Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-28 lloveras_2020_Albert.tex
Edits by Albert, Viernes 27/Dic

\albert{For both rotations it is readily seen that the integrated radiative loss of the loops, measured by the quantity $\phi_r$, is largest for loops of type 0, smaller for loops of type I, and smalest for loops of type II . This is mainly due to the fact that in the range of sensitivity of the AUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$. Indeed, according to Table 1, loops of type 0 have the lowest temperature of them all and closest to $\Tc$, for both rotations.}

@@

\albert{The characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.0 \times 10^5\,\erg\cminvs\s^{-1}$, depending on the rotatin and the type of loop. These values are consistent with those reported by \citet{maccormack_2017}.}

>>>>

\albert{For both rotations it is readily seen that the integrated radiative loss, measured by the quantity $\phi_r$, is largest for loops of type 0, smaller for loops of type I, and smallest for loops of type II . This is mainly due to the fact that in the range of sensitivity of the AUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$. Indeed, according to Table 1, loops of type 0 have the lowest temperature of them all and closest to $\Tc$, for both rotations.}

@@

\albert{The characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.0 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of loop. These values are similar to those reported by \citet{maccormack_2017}.}
